\newacronym{rfid}{RFID}{Radio Frequency Identification}

\newacronym{ai}{AI}{Artificial Intelligence refers to the development of 
computer systems that can perform tasks that would typically require 
human intelligence to complete, such as learning, problem-solving, decision 
making, and language understanding.}

\newacronym{neuro}{neural network}{A neural network is a type of machine 
learning algorithm inspired by the structure and function of the human 
brain. It consists of interconnected nodes or "neurons" that work together 
to process and analyze data, allowing the network to learn and make predictions 
based on that data. Neural networks are commonly used in a wide range of 
applications, including image and speech recognition, natural 
language processing, and autonomous vehicles.}

\newacronym{vrm}{VRM}{Virtual Reality Model is a file format used in the 
context of 3D virtual reality environments. It is similar to other 3D model 
file formats such as OBJ, FBX, and STL, but is specifically designed for 
use in virtual reality applications.}

\newacronym{vr}{VR}{Virtual Reality is a computer-generated simulation of 
a three-dimensional environment or experience that can be interacted with 
by a person through the use of specialized hardware, such as a VR headset 
or gloves. The technology creates a realistic, immersive experience that 
can simulate sensory experiences such as sight, sound, and touch.}

\newacronym{cmu}{cmu chunker programm}{The CMU chunker program is a tool 
used in natural language processing (NLP) that is designed to break down 
complex sentences into smaller syntactic units, known as "chunks". This 
helps to simplify the text and make it easier for algorithms to analyze 
and understand.}

\newacronym{hadoop}{Hadoop}{Hadoop is an open-source software framework 
used for distributed storage and processing of large datasets across 
clusters of computers. It is designed to handle big data by breaking 
it down into smaller chunks and distributing it across multiple nodes 
in a cluster for parallel processing.}

\newacronym{spark}{Spark}{Apache Spark is an open-source 
distributed computing system used for large-scale data 
processing. It provides a fast and flexible data processing 
engine that can handle a wide range of workloads, including 
batch processing, real-time streaming, machine learning, 
and graph processing.}

\newacronym{h264}{H.264}{H.264 is a video compression format 
that is used for recording, compression, and distribution of 
high-definition video content. It is a popular and widely used 
format that offers high-quality video at relatively low bit rates, 
making it suitable for streaming over the internet and storing on 
portable devices. H.264 is also known as AVC (Advanced Video Coding) 
and is used by many streaming services and video players.}

\newacronym{mpeg}{MPEG-4}{MPEG-4 is a video compression format that is 
used for encoding and decoding audiovisual content. It is designed to 
provide high-quality video at relatively low bit rates, making it 
suitable for streaming over the internet and storing on portable 
devices. MPEG-4 supports a wide range of multimedia content, including 
video, audio, and still images, and includes advanced features such as 
interactivity and content protection. It is commonly used for video 
streaming, online video sharing, and multimedia messaging.}


% Usage:
% \gls{label} lowercase in text
% \Gls{label} Uppercase in text
% \newacronym{label}{abbrev}{full}
% \newglossaryentry{label}{settings}


